taxize: taxonomic search and retrieval in R

### 2013-10-01 f1000_rev/taxize_ms.Rnw

\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
\usepackage{alltt}
\newcolumntype{L}{>{\raggedright\arraybackslash}m{5cm}} % creates now column type to wrap text

\usepackage{listings}

@@

<<setup, include=FALSE, cache=FALSE, size='scriptsize'>>=
## set global chunk options
opts_chunk$set(fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment=NA)
@

@@

<<installtaxizecran, eval=FALSE, size='scriptsize'>>=
install.packages("taxize")
@

<<loadtaxize, size='scriptsize'>>=
library(taxize)
@

@@

<<resolvenames, results='hide', cache=TRUE, size='scriptsize'>>=
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
@

<<resolvenames1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
temp[ , -c(1,4)]
@

@@

<<tnrs, results='hide', cache=TRUE, size='scriptsize'>>=
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames)[ , -c(5:7)]
@

<<tnrs1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
tnrs(query = mynames)[ , -c(5:7)]
@

@@

<<synonyms, results='hide', cache=TRUE, message=FALSE, warning=FALSE, comment=NA, size='scriptsize'>>=
library(plyr)
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus", "Helianthus annuus var. lenticularis", "Helianthus annuus var. macrocarpus", "Helianthus annuus var. texanus")
tsn <- get_tsn(mynames)
ldply(tsn, itis_acceptname)
@

<<synonyms1, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE, comment=NA, size='scriptsize'>>=
library(plyr)
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus", "Helianthus annuus var. lenticularis", "Helianthus annuus var. macrocarpus", "Helianthus annuus var. texanus")
tsn <- get_tsn(mynames)
ldply(tsn, itis_acceptname)
@

@@

<<itisclass, results='hide', cache=TRUE, size='scriptsize'>>=
specieslist <- c("Abies procera","Pinus contorta")
classification(specieslist, db = 'itis')
@

<<itisclass1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
specieslist <- c("Abies procera","Pinus contorta")
classification(specieslist, db = 'itis')
@

@@

<<taxname, results='hide', cache=TRUE, size='scriptsize'>>=
tax_name(query = "Helianthus annuus", get = "family", db = "itis")
tax_name(query = "Helianthus annuus", get = "family", db = "ncbi")
@

<<taxname1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
tax_name(query = "Helianthus annuus", get = "family", db = "itis")
tax_name(query = "Helianthus annuus", get = "family", db = "ncbi")
@

@@

<<interactive, results='hide', cache=TRUE, size='scriptsize'>>=
get_tsn(searchterm = "Heliastes", searchtype = "sciname")
@

<<interactive1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
get_tsn(searchterm = "Heliastes", searchtype = "sciname")
@

@@

<<interactive_many, results='hide', cache=TRUE, size='scriptsize'>>=
splist <- c("annona cherimola", 'annona muricata', "quercus robur",
  	"shorea robusta", "pandanus patina", "oryza sativa", "durio zibethinus")
get_tsn(searchterm = splist, searchtype = "sciname")
@

<<interactive_many1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
splist <- c("annona cherimola", 'annona muricata', "quercus robur",
    "shorea robusta", "pandanus patina", "oryza sativa", "durio zibethinus")
get_tsn(searchterm = splist, searchtype = "sciname")
@

@@

<<interactive_na, results='hide', cache=TRUE, size='scriptsize'>>=
get_uid(sciname = c("Chironomus riparius", "aaa vva"))
@

<<interactive_na1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
get_uid(sciname = c("Chironomus riparius", "aaa vva"))
@

@@

<<downstream, results='hide', cache=TRUE, size='scriptsize'>>=
col_downstream(name = "Apis", downto = "Species")[[1]]
@

<<downstream1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
col_downstream(name = "Apis", downto = "Species")[[1]]
@

@@

<<iucn, results='hide', cache=TRUE, size='scriptsize'>>=
ia <- iucn_summary(c("Panthera uncia", "Lynx lynx"))
iucn_status(ia)
@

<<iucn1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
ia <- iucn_summary(c("Panthera uncia", "Lynx lynx"))
iucn_status(ia)
@

@@

<<genbank_two, results='hide', cache=TRUE, size='scriptsize'>>=
out[grep("RAG1", out$genesavail, ignore.case = TRUE), -3]
@

<<genbank_two1, echo=FALSE, cache=TRUE, size='scriptsize'>>=
out[grep("RAG1", out$genesavail, ignore.case = TRUE), -3]
@

@@

<<tax_match, results='hide', cache=TRUE, tidy=FALSE, size='scriptsize'>>=
A <- "gammarus roeseli"

@@

B1[match(A, B1)]
@

<<tax_match1, echo=FALSE, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
B1[match(A, B1)]
@

<<tax_match2, results='hide', cache=TRUE, tidy=FALSE, size='scriptsize'>>=
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B2]
@

<<tax_match3, echo=FALSE, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B2]
@

<<tax_match4, results='hide', cache=TRUE, tidy=FALSE, size='scriptsize'>>=
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B3]
@

<<tax_match5, echo=FALSE, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B3]
@

@@

<<tax_agg, results='hide', cache=TRUE, tidy=FALSE, size='scriptsize'>>=
data(dune, package = 'vegan')
df <- dune[ , c(1,3:4)]
colnames(df) <- c("Bellis perennis", "Juncus bufonius", "Juncus articulatus")
head(df)
@

<<tax_agg1, echo=FALSE, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
head(df)
@

<<tax_agg2, results='hide', cache=TRUE, tidy=FALSE, size='scriptsize'>>=
agg <- tax_agg(df, rank = 'family', db = 'ncbi')
agg
@

<<tax_agg3, echo=FALSE, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
agg
@

<<tax_agg4, results='hide', cache=TRUE, tidy=FALSE, size='scriptsize'>>=
head(agg$x)
@

<<tax_agg5, echo=FALSE, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
head(agg$x)
@

>>>>

\newcolumntype{L}{>{\raggedright\arraybackslash}m{5cm}} % creates now column type to wrap text

@@

<<setup, include=FALSE, cache=FALSE, size='scriptsize'>>=
## set global chunk options
opts_chunk$set(fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment='#')
@

@@

<<installtaxizecran, eval=FALSE, size='scriptsize'>>=
install.packages("taxize")
library(taxize)
@

<<loadtaxize, eval=TRUE, echo=FALSE, size='scriptsize'>>=
library(taxize)
@

@@

<<resolvenames, cache=TRUE, size='scriptsize'>>=
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
@

@@

<<tnrs, cache=TRUE, size='scriptsize'>>=
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames)[ , -c(5:7)]
@

@@

<<synonyms, cache=TRUE, message=FALSE, warning=FALSE, size='scriptsize'>>=
library(plyr)
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus", "Helianthus annuus var. lenticularis", "Helianthus annuus var. macrocarpus", "Helianthus annuus var. texanus")
tsn <- get_tsn(mynames)
ldply(tsn, itis_acceptname)
@

@@

<<itisclass, cache=TRUE, size='scriptsize'>>=
specieslist <- c("Abies procera","Pinus contorta")
classification(specieslist, db = 'itis')
@

@@

<<taxname, cache=TRUE, size='scriptsize'>>=
tax_name(query = "Helianthus annuus", get = "family", db = "itis")
tax_name(query = "Helianthus annuus", get = "family", db = "ncbi")
@

@@

<<interactive, cache=TRUE, size='scriptsize'>>=
get_tsn(searchterm = "Heliastes", searchtype = "sciname")
@

@@

<<interactive_many, cache=TRUE, size='scriptsize'>>=
splist <- c("annona cherimola", 'annona muricata', "quercus robur",
  	"shorea robusta", "pandanus patina", "oryza sativa", "durio zibethinus")
get_tsn(searchterm = splist, searchtype = "sciname")
@

@@

<<interactive_na, cache=TRUE, size='scriptsize'>>=
get_uid(sciname = c("Chironomus riparius", "aaa vva"))
@

@@

<<downstream, cache=TRUE, size='scriptsize'>>=
col_downstream(name = "Apis", downto = "Species")[[1]]
@

@@

<<iucn, cache=TRUE, size='scriptsize'>>=
ia <- iucn_summary(c("Panthera uncia", "Lynx lynx"))
iucn_status(ia)
@

@@

<<genbank_two, cache=TRUE, size='scriptsize'>>=
out[grep("RAG1", out$genesavail, ignore.case = TRUE), -3]
@

@@

<<tax_match, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
A <- "gammarus roeseli"

@@

B1[match(A, B1)]
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B2]
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B3]
@

@@

<<tax_agg,, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
data(dune, package = 'vegan')
df <- dune[ , c(1,3:4)]
colnames(df) <- c("Bellis perennis", "Juncus bufonius", "Juncus articulatus")
head(df)
@

<<tax_agg2, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
agg <- tax_agg(df, rank = 'family', db = 'ncbi')
agg
@

<<tax_agg4, cache=TRUE, tidy=FALSE, size='scriptsize'>>=
head(agg$x)
@
